\documentclass[a4paper, 10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}

\begin{document}

\noindent\textbf{Naman Verma}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology Kanpur, India\\
E-Mail: \href{namanv@cse.iitk.ac.in}{namanv@cse.iitk.ac.in}, \href{namanva@iitk.ac.in}{namanva@iitk.ac.in}

\par\noindent\rule{\textwidth}{0.4pt}
\par\noindent\rule{\textwidth}{0.4pt}

\section*{Education}

\begin{tabular}{ |c|c|c|c| } 
    \hline
    Matriculation & 2014 & Sacred Heart Convent School, Ludhiana & CGPA: 9.6 \\
    \hline
    Intermediate & 2016 & Shri Guru Gobind Singh School, Chandigarh & 93.4\% \\ 
    \hline
    B.Tech & 2020 (expected) & Indian Institute of Technology, Kanpur & CPI: 8.04\\ 
    \hline
\end{tabular}

\section*{Course Details}

\begin{tabular}{ |c|c|c| } 
    \hline
    \textbf{Semester} & \textbf{Total Credits} & \textbf{Highlighted Courses} \\
    \hline
    Aug 2016 - Nov 2016 & 50 & ESC101A \\
    \hline
    Jan 2017 - Apr 2017 & 48 & MTH102A \\
    \hline
    Aug 2017 - Nov 2017 & 53 & CS201A, CS202A, CS203B \\
    \hline
    Jan 2018 - Apr 2018 & 58 & CS220A, CS251A, ESO207A, MSO201A\\
    \hline
\end{tabular}

\section*{Skills}

Programming Languages: C, C++, Python, Scripting Languages (Bash, Awk).\\
Popular Software: Autodesk Fusion 360, Adobe Photoshop.

\section*{Awards and Achievements}

\begin{itemize}
    \item AIR 148 in JEE Advanced 2016, from among 150k students.
    \item AIR 256 in NTSE, National Level in 2012.
    \item Selected for KVPY Scholarship in 2016.
    \item Scored 275 marks in JEE Mains 2016 (highest marks from Chandigarh).
\end{itemize}

\section*{Course Projects and Talks}

\begin{itemize}
    \item \textbf{ART106A}: Published a booklet on how to draw Anime Characters.
    \item \textbf{PSY499A}: Talk on how mind interprets and parses relative clauses in a sentence, and how the semantics of relative clauses is extracted.
    \item \textbf{TA201A}: Made a miniature model of a Forklift, with mechanical controls to lift objects using a pair of front forks, right from the pre-production stage, involving designing using Fusion 360, and learning and applying various manufacturing processes like casting, welding, brazing, etc.
\end{itemize}

\section*{Positions of Responsibility}
\begin{itemize}
    \item \textbf{Student Guide under Counselling Service:} Responsible for accommodating and introducing a group of 5 incoming students into their new lives in IIT Kanpur.
    \item \textbf{Member of Core Group, Vox Populi (2016-present):} Part of the Institute Journalism Body since my first year. Played a crucial role in the coverage of the 2016 Inter IIT Sports Meet, especially the video department.
\end{itemize}

\end{document}
